Model Finding for (Co)recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-05 tex/main.tex
Bug fixes, converge on terminologies.

\newcommand{\pnone}{\con{none}}
\newcommand{\ptrue}{\con{pos}}
\newcommand{\pfalse}{\con{neg}}
\newcommand{\pol}{\con{pol}}

@@

%\newcommand\concret{\con{a}}
%\newcommand\concret{\con{c}}
\newcommand\concret{\gamma} %%% from the abstract interpretation literature

\newcommand{\boolop}{\oplus}
\newcommand{\forallf}[1]{\forall_{\!#1\:}}
\newcommand{\fnull}{\emptyset}
\newcommand{\vecfarg}[1]{\vec{\concret}_{\vthinspace#1}}
\newcommand{\farg}[1]{\concret_{\vthinspace#1}}
\newcommand{\fargx}[2]{\concret^{\vthinspace#2}_{\vthinspace#1}}
\newcommand{\fargsort}[1]{\upsilon_{\vthinspace#1}}

@@

Recent techniques~\cite{GeDeM-CAV-09, ReyEtAl-1-RR-13} 
have focused on finding models for quantified formulas in SMT.
Ge and de Moura \cite{GeDeM-CAV-09} presented a complete instantiation-based
procedure for formulas in the \emph{essentially uninterpreted} fragment.
This fragment is limited to universally quantified formulas where all
occurrences of variables occur as direct subterms of uninterpreted
functions. For example, the formula $\forall x%\typ{\sortint} --- the sort is not important, right?
.\;\, \con{f}( x )
\teq \con{g}( x ) + 5$ is in the essentially uninterpreted fragment.
% since all
% occurrences of $x$ occur beneath uninterpreted functions $\con{f}$ and
% $\con{g}$.
Other syntactic criteria are identified in this paper that extend
this fragment slightly, including cases when variables occur as arguments of
arithmetic predicates. The techniques in~Reynolds et al.\
\cite{ReyEtAl-1-RR-13} can be used for finding finite models for quantified
formulas over uninterpreted types as well as types having a fixed finite
interpretation, such as fixed-width bitvectors and enumerated datatypes.
Finite model finding techniques can
find a model for the formula $\forall x\typ{\tau} y\typ{\tau}.\;\, \neg x \teq
y \vee \con{f}( x ) \teq \con{f}( y )$ where the uninterpreted type $\tau$ is
interpreted as a finite set and $\con{f}$ as injective finite map.
\jb{Weird example. This formula is a tautology of EUF! Maybe you put the
negation at the right place?}

@@

%In this paper, we associate quantified formulas with uninterpreted functions (informally, those whose semantics they define).
In this paper, we consider \emph{annotated quantifed formulas} of the form
$\forallf{a} \vec x.\; \varphi$, where the annotation~$a$ is either
an uninterpreted function $\con{f} \in \sfuns{\Sigma}$ or the special symbol
$\fnull$.
Given $\con{f} : \tau_1 \times \ldots \times \tau_n \rightarrow \tau$,
an annotated
quantified formula $\forallf{\con{f}} \vec x.\; \varphi$ is a \emph{function definition}
(\,\emph{for $\con{f}$}\vthinspace) if $\vec x$ is a tuple of variables of type
$\tau_1, \ldots, \tau_n$ and $\forallf{\con{f}} \vec x.\; \varphi$ is equivalent to
$\forall \vec x.\;\, \con{f}( \vec x ) \teq t$ for some $t$. We write $\forall \vec
x.\; \varphi$ as shorthand for $\forallf{\fnull} \vec x.\; \varphi$, and $\exists
\vec x. \varphi$ as shorthand for $\neg \forall \vec x.\; \neg \varphi$.

\begin{definition}%
\rm
A formula $\varphi$ is in \emph{definitional form with respect to} functions $\{
\con{f}_1, \ldots, \con{f}_n \}$ if it is of the form
%
%\kern-\abovedisplayskip
%\kern+\abovedisplayshortskip
%
\begin{equation} \label{eq:wdf}
(\forallf{\con{f}_1} \vec x_1.\; \varphi_1) \wedge \ldots \wedge (\forallf{\con{f}_n} \vec x_n.\; \varphi_n) \wedge \psi
\end{equation}
%
where $\con{f}_1, \ldots, \con{f}_n$ are not $\fnull$ and distinct, 
and $\psi$ contains no function definitions.
We call $\psi$ the \emph{conjecture} of $\varphi$.
\ct{Don't we need additional restrictions on the $\varphi_i$'s here?
(E.g., they are quantifier-free, or perhaps existential or containing only let binders.)}
\end{definition}

@@

A set of function definitions $\{ \varphi_1, \ldots, \varphi_n \}$ 
is \emph{admissible} (\emph{in $T$}) if $\varphi_1 \wedge \ldots \wedge \varphi_n$ is $T$-satisfiable.
For example, $\{ \forallf{\con{f}} x.\;\, \con{f}( x ) \teq 0 \}$
and $\{ \forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ) \}$ are admissible,
whereas $\{ \forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ) + 1 \}$ is not.
\ajr{revise}

@@

Let us fix a signature $\Sigma$, a $\Sigma$-formula
$\varphi$ in definitional form with respect to functions $\sfundefs{\Sigma}$,
whose definitions are admissible.
%We may translate $\varphi$ into a equisatisfiable formula $\psi$ for which known model-finding procedures~\cite{GeDeM-CAV-09, ReyEtAl-1-RR-13} are applicable.
This section presents a method for constructing an extended signature
$\extendsig{ \Sigma }$ and a $\extendsig{ \Sigma }$-formula $\psi$ such that
$\varphi$ and $\psi$ are equisatisfiable.
\jb{Equisatisfiability as defined in Sect.\ 2 requires the same $\Sigma$ and
the same $T$ for both formulas, which isn't the case here.}
The intuition behind this translation
is to use an uninterpreted type \ct{to be defined} to abstract the set of
\relax{relevant} tuples for each recursive function $\con{f}$ and restrict the
quantification of the function definition for $\con{f}$ to a variable of this
type. Informally, the relevant tuples $\vec t$ of a function $\con{f}$ are the
ones for which the interpretation of $\con{f}( \vec t )$ is relevant to the
satisfiability of $\varphi$.

@@

In more detail, 
suppose our signature $\Sigma$ contains a set of defined function symbols $\sfundefs{\Sigma} \subseteq \sfuns{\Sigma}$.
We extend the signature of $\Sigma$ to a signature $\extendsig{\Sigma}$ containing the following additional definitions.
For each $\con{f} : \tau_1 \times \ldots \times \tau_n \rightarrow \tau \in \sfundefs{\Sigma}$,
the signature $\extendsig{\Sigma}$ includes
\begin{itemize}
\item an uninterpreted \emph{abstract type} $\fargsort{\con{f}}$;
\item $n$ uninterpreted \emph{concretization functions} $\fargx{\con{f}}{1} : \fargsort{\con{f}} \rightarrow \tau_1$, \ldots, $\fargx{\con{f}}{n} : \fargsort{\con{f}} \rightarrow \tau_n$.
\end{itemize}
%The interpretation of uninterpreted sort $\fargsort{\con{f}}$ will denote the elements (tuples) on which the function $\con{f}$ is applied.
%The role of the uninterpreted functions $\farg{\con{f}}^1$, $\ldots$, $\farg{\con{f}}^n$ will be discussed more in the following.

The procedure $\conv$ in Figure~\ref{fig:encoding} translates the $\Sigma$-formula
$\varphi$ into an $\extendsig{\Sigma}$-formula.
This calls the subprocedure $\conv_0$, which takes two arguments:\ the term $t$
to translate and a \emph{polarity} $p$ (either $\ptrue$, $\pfalse$, or
$\pnone$). It returns a pair $( r,\, D )$, where $r$ is a term of
type $\tau$ and $D$ is a set of formulas.
\jb{Explain r and D here briefly.}
%The role of $D$ is to ensure that
%the (restricted) function definition for $\con{f}$ includes certain tuples in
%its domain, which we explain more in the following.

The translation modifies $\varphi$ in two main ways. First, it restricts the
quantification on function definitions for $\con{f}$ to the corresponding
uninterpreted type $\fargsort{\con{f}}$ and inserts appropriate . Second, it augments $\varphi$ with
additional constraints of the form $\exists z\typ{\fargsort{\con{f}}}. (
\vecfarg{\con{f}}( z ) \teq \vec t )$ which ensure that this restriction for
the defintion $\con{f}$ covers all relevant tuples of terms, namely the ones
for which an $\con{f}$-application exists and is relevant to the satisfiability
of the current branch of $\varphi$.

@@

\begin{theorem}
If $\varphi$ be a $\Sigma$-formula that is in definitional form with respect to functions $\sfundefs{\Sigma}$,
and the set of function definitions corresponding to functions in $\sfundefs{\Sigma}$ is admissible,
then $\varphi$ and $\conv( \varphi )$ are equisatisfiable.
\end{theorem}
\begin{proof}
(Sketch)  First, we show that if $\varphi$ has a model $\I$, then $\conv( \varphi )$ has a model $\J$.
Let $\J$ be the $\extendsig{\Sigma}$-interpretation that interprets all types $\tau \in \ssorts{\Sigma}$ as $\tau^\I$,
all functions $\con{f} \in \sfuns{\Sigma}$ as $\con{f}^\I$,
and for each function $\con{f}$ of type $\tau_1 \times \ldots \tau_n \rightarrow \tau$ in $\sfundefs{\Sigma}$, 
interprets $\fargsort{\con{f}}$ as a tuple of values of type $\tau_1^\I \times \ldots \times \tau_n^\I$,
and each $\fargx{\con{f}}{i}$ as the $i^{th}$ projection on such tuples for each $i = 1, \ldots, n$.
Note that $\J$ satisfies \emph{every} constraint of the form $\exists z\typ{\fargsort{\con{f}}}. ( \vecfarg{\con{f}}( z ) \teq \vec t )$,
since by our construction of $\J$ there exists a $z$ such that $z^\J = \vec t^\J$.
By case analysis it follows that $\conv_0$ maintains the invariant that
if $\conv_0( t\typ{\Bool}, \ptrue )$ returns $( r\typ{\Bool}, D )$,
then $\I$ satisfies $t$ if and only if $\J$ satisfies $r$.
Thus, we conclude $\J$ is a model of $\conv( \varphi )$.

Second, we show that if $\conv( \varphi )$ has a model $\I$, then $\varphi$ has a model $\J$.

\end{proof}

@@

When reading this input, 
\cvc adds the (annotated) quantified formula $\forallf{s} x.\;\, s( x ) \teq \lite( x \leq 0, 0, s( x-1 ) )$ to its list of assertions,
which after rewriting becomes $\forallf{s} x.\;\, \lite( x \leq 0, s( x ) \teq 0, s( x ) \teq s( x-1 ) )$.
If \cvc's finite model finding mode for recursive functions is enabled (using the command line parameter ``--fmf-fun"),
then it will replace its list of known assertions based on the conversion $\conv$ before checking for satisfiability.
Note that this option is model-sound \ct{define?} only if the functions provided in the input are admissible.

>>>>

\newcommand{\pnone}{\con{none}}
\newcommand{\ptrue}{\con{true}}
\newcommand{\pfalse}{\con{false}}
\newcommand{\pol}{\con{pol}}

@@

\newcommand{\boolop}{\oplus}
\newcommand{\forallf}[1]{\forall_{\!#1\:}}
\newcommand{\fnull}{\emptyset}
\newcommand{\farg}[1]{a_{#1}}
\newcommand{\vecfarg}[1]{\vec{a}_{#1}}
\newcommand{\fargsort}[1]{\upsilon_{#1}}

@@

Recent techniques~\cite{GeDeM-CAV-09, ReyEtAl-1-RR-13} 
have focused on finding models for quantified formulas in SMT.
Ge and de Moura \cite{GeDeM-CAV-09} presented a complete instantiation-based
procedure for formulas in the \emph{essentially uninterpreted} fragment.
This fragment is limited to universally quantified formulas where all
occurrences of variables occur as direct subterms of uninterpreted
functions. For example, the formula $\forall x%\typ{\sortint} --- the sort is not important, right?
.\;\, \con{f}( x )
\teq \con{g}( x ) + 5$ is in the essentially uninterpreted fragment.
% since all
% occurrences of $x$ occur beneath uninterpreted functions $\con{f}$ and
% $\con{g}$.
Other syntactic criteria are identified in this paper that extend
this fragment slightly, including cases when variables occur as arguments of
arithmetic predicates. The techniques in~Reynolds et al.\
\cite{ReyEtAl-1-RR-13} can be used for finding finite models for quantified
formulas over uninterpreted types as well as types having a fixed finite
interpretation, such as fixed-width bitvectors and enumerated datatypes.
Finite model finding techniques can
find a model for the formula $\forall x\typ{\tau} y\typ{\tau}.\;\, x \teq
y \vee \neg \con{f}( x ) \teq \con{f}( y )$ where the uninterpreted type $\tau$ is
interpreted as a finite set and $\con{f}$ as injective finite map.

@@

In this paper, we consider \emph{annotated quantifed formulas} of the form
$\forallf{a} \vec x.\; \varphi$, where the annotation~$a$ is either
an uninterpreted function $\con{f} \in \sfuns{\Sigma}$ or the special symbol
$\fnull$.
Given $\con{f} : \tau_1 \times \ldots \times \tau_n \rightarrow \tau$,
an annotated
quantified formula $\forallf{\con{f}} \vec x.\; \varphi$ is a \emph{function definition}
(\,\emph{for $\con{f}$}\vthinspace) if $\vec x$ is a tuple of variables of type
$\tau_1, \ldots, \tau_n$ and $\varphi$ is a (quantifier-free) formula equivalent to
$\con{f}( \vec x ) \teq t$ for some $t$. We write $\forall \vec
x.\; \varphi$ as shorthand for $\forallf{\fnull} \vec x.\; \varphi$, and $\exists
\vec x. \varphi$ as shorthand for $\neg \forall \vec x.\; \neg \varphi$.
For a formula $\varphi$, 
we write $\varphi[\vec t/\vec x]$ to denote the result of replacing all occurrences of $\vec x$ with $\vec t$.

\begin{definition}%
\rm
A formula $\varphi$ is in \emph{definitional form with respect to} functions $\{
\con{f}_1, \ldots, \con{f}_n \}$ if it is of the form
%
%\kern-\abovedisplayskip
%\kern+\abovedisplayshortskip
%
\begin{equation} \label{eq:wdf}
(\forallf{\con{f}_1} \vec x_1.\; \varphi_1) \wedge \ldots \wedge (\forallf{\con{f}_n} \vec x_n.\; \varphi_n) \wedge \psi
\end{equation}
%
where $\con{f}_1, \ldots, \con{f}_n$ are not $\fnull$ and distinct, 
and $\psi$ contains no function definitions.
We call $\psi$ the \emph{conjecture} of $\varphi$.
%\ct{Don't we need additional restrictions on the $\varphi_i$'s here?
%(E.g., they are quantifier-free, or perhaps existential or containing only let binders.)}
% Now fixed above -ajr
\end{definition}

@@

\begin{definition}
Given a set of function definitions $\mathcal{D} = \{ \forallf{f_1} \vec x. \varphi_1, \ldots, \forallf{f_n} \vec x. \varphi_n \}$,
a formula $\varphi$ is \emph{closed under function expansion with respect to $\mathcal{D}$} if
\begin{eqnarray}
\varphi \text{ entails } \displaystyle\bigwedge\limits_{i=1}^n \{ \varphi_i[ \vec t / \vec x ] \mid f_i( \vec t ) \in \terms( \varphi ) \}
\end{eqnarray}
The set $\mathcal{D}$ is \emph{admissible} if whenever there exists a model for $\varphi$ that is closed under function expansion,
there exists a model for $\varphi \wedge \forallf{f_1} \vec x. \varphi_1 \wedge \ldots \wedge \forallf{f_n} \vec x. \varphi_n$.
\end{definition}

For instance, the set $\{ \forallf{f} \vec x. f( x ) \teq 0 \}$ is admissible.
A set of admissible function definitions can include definitions of non-terminating functions, e.g.
$\{ \forallf{f} x^\sortint. f( x ) \teq f( x - 1 ) \}$ or even $\{ \forallf{f} x. f( x ) \teq f( x ) \}$ are admissible.
On the other hand, the set $\{ \forallf{f} x. f( x ) \teq f( x ) + 1 \}$ is not admissible, 
since the empty set of formulas is closed under function expansion with respect to this set,
and there is no model satisfying $\forallf{f} x. f( x ) \teq f( x ) + 1$.
Consider the set $\{ \forallf{f} x. f( x ) \teq f( x ), \forallf{g}. \lite( \neg f( x ) \teq 5, g( x ) \teq g( x ) + 1, g( x ) \teq f( x ) ) \}$.
While this set has a model where $f$ and $g$ are interpreted as the constant $5$, it is not admissible
since the formula $f( 0 ) \teq 4$ is closed under function expansion with respect to this set,
but there exists no interpretation satisfying both $f( 0 ) \teq 4$ and $\forallf{g}. \lite( \neg f( x ) \teq 5, g( x ) \teq g( x ) + 1, g( x ) \teq f( x ) )$.

@@

Let us fix a signature $\Sigma$, a $\Sigma$-formula
$\varphi$ in definitional form with respect to functions $\sfundefs{\Sigma}$,
whose definitions are admissible.
%We may translate $\varphi$ into a equisatisfiable formula $\psi$ for which known model-finding procedures~\cite{GeDeM-CAV-09, ReyEtAl-1-RR-13} are applicable.
This section presents a method for constructing an extended signature
$\extendsig{ \Sigma }$ and a $\extendsig{ \Sigma }$-formula $\psi$ such that
$\varphi$ and $\psi$ are equisatisfiable.
\jb{Equisatisfiability as defined in Sect.\ 2 requires the same $\Sigma$ and
the same $T$ for both formulas, which isn't the case here.}
The intuition behind this translation
is to use an uninterpreted type \ct{to be defined} to abstract the set of
\emph{relevant} tuples for each recursive function $\con{f}$ and restrict the
quantification of the function definition for $\con{f}$ to a variable of this
type. Informally, the relevant tuples $\vec t$ of a function $\con{f}$ are the
ones for which the interpretation of $\con{f}( \vec t )$ is relevant to the
satisfiability of $\varphi$.

@@

In more detail, 
say our signature $\Sigma$ contains a set of defined function symbols $\sfundefs{\Sigma} \subseteq \sfuns{\Sigma}$.
We extend the signature of $\Sigma$ to a signature $\extendsig{\Sigma}$ containing the following additional definitions.
For each $\con{f} \in \sfundefs{\Sigma}$ of type $\tau_1 \times \ldots \times \tau_n \rightarrow \tau$, 
the signature $\extendsig{\Sigma}$ includes:
\begin{enumerate}
\item[-] an uninterpreted type $\fargsort{\con{f}}$, and
\item[-] a vector of $n$ uninterpreted functions $\farg{\con{f}}^1$, $\ldots$, $\farg{\con{f}}^n$ of type $(\fargsort{\con{f}} \rightarrow \tau_1)$, $\ldots$, $(\fargsort{\con{f}} \rightarrow \tau_n)$.
\end{enumerate}
%The interpretation of uninterpreted sort $\fargsort{\con{f}}$ will denote the elements (tuples) on which the function $\con{f}$ is applied.
%The role of the uninterpreted functions $\farg{\con{f}}^1$, $\ldots$, $\farg{\con{f}}^n$ will be discussed more in the following.

Given the extended signature, we run the procedure $\conv$ in Figure~\ref{fig:encoding} on $\varphi$.
This calls the subprocedure $\conv_0$, which takes two arguments: the term $t$ to translate, and a \emph{polarity} $p$ (either $\ptrue$, $\pfalse$, or $\pnone$).
It returns a pair of the form $( r, D )$, where $r$ is a term of type $\tau$, and $D$ is a set of formulas.
%The role of $D$ is to ensure that the (restricted) function definition for $\con{f}$ includes certain tuples in its domain, which we explain more in the following.
At a high level, the translation modifies $\varphi$ in two ways.
First, it restricts the quantification on function definitions for $\con{f}$ to the corresponding uninterpreted type $\fargsort{\con{f}}$.
Second, it augments $\varphi$ with additional constraints of the form $\exists z\typ{\fargsort{\con{f}}}. ( \vecfarg{\con{f}}( z ) \teq \vec t )$
which ensure that this restriction for the defintion $\con{f}$ covers all relevant tuples of terms,
namely the ones for which an $\con{f}$-application exists and is relevant to the satisfiability of the current branch of $\varphi$.

@@

\begin{theorem}
If $\varphi$ is a $\Sigma$-formula that is in definitional form with respect to functions $\sfundefs{\Sigma}$,
and the set of function definitions $\mathcal{D}$ corresponding to functions in $\sfundefs{\Sigma}$ is admissible,
then $\varphi$ and $\conv( \varphi )$ are equisatisfiable.
\end{theorem}
\begin{proof}
(Sketch)  First, we show that if $\varphi$ is satisfied by $\Sigma$-interpretation $\I$, then $\conv( \varphi )$ is satisfied by a $\extendsig{\Sigma}$-interpretation $\J$.
Let $\J$ be the $\extendsig{\Sigma}$-interpretation that interprets all types $\tau \in \ssorts{\Sigma}$ as $\tau^\I$,
all functions $\con{f} \in \sfuns{\Sigma}$ as $\con{f}^\I$,
and for each function $\con{f}$ of type $\tau_1 \times \ldots \tau_n \rightarrow \tau$ in $\sfundefs{\Sigma}$, 
interprets $\fargsort{\con{f}}$ as a tuple of values of type $\tau_1^\I \times \ldots \times \tau_n^\I$,
and each $\farg{\con{f}}^i$ as the $i^{th}$ projection on such tuples for each $i = 1, \ldots, n$.
Note that $\J$ satisfies \emph{every} constraint of the form $\exists z\typ{\fargsort{\con{f}}}. ( \vecfarg{\con{f}}( z ) \teq \vec t )$,
since by our construction of $\J$ there exists a $z$ such that $z^\J = \vec t^\J$.
By case analysis it follows that $\conv_0$ maintains the invariant that
if $\conv_0( t\typ{\Bool}, \ptrue )$ returns $( r\typ{\Bool}, D )$,
then $\I$ satisfies $t$ if and only if $\J$ satisfies $r$.
Thus, we conclude $\J$ is a model of $\conv( \varphi )$.

Second, we show that if $\conv( \varphi )$ is satisfied by a $\extendsig{\Sigma}$-interpretation $\I$, then $\varphi$ is satisfied by $\Sigma$-interpretation $\J$.
Since $\varphi$ is in definitional form with respect to functions defined by $\mathcal{D}$, we know $\varphi$ is of the form $\mathcal{D} \wedge \varphi_0$.
We first argue that $\I$ satisfies a $\Sigma$-formula $\psi$ that is closed under function expansion with respect to $\mathcal{D}$,
and where $\psi$ entails $\varphi_0$.

Since there exists a model for $\psi$ that is closed under function expansion with respect to $\mathcal{D}$, 
then since $\mathcal{D}$ is admissible,
by definition there exists a model for $\psi \wedge \mathcal{D}$, which entails $\mathcal{D} \wedge \varphi_0$, which is $\varphi$.
\end{proof}

Let us revisit the translated formula~(\ref{eq:ex-after}) from Example~\ref{ex:translation}.
This formula is unsatisfiable if and only if formula~(\ref{eq:ex-before}) is unsatisfiable since $\fargsort{f}$ can be interpreted as $\sortint$,
and $\farg{f}$ can be interpreted as the identity function.
Conversely, we claim formula~(\ref{eq:ex-after}) is satisfiable if and only if formula~(\ref{eq:ex-before}) is satisfiable,
noting that the set $\{ \forall_{s} x\typ{\sortint}. ite( x \leq 0, s(x) \teq 0, s( x ) \teq x + s( x-1 ) ) \}$ is admissble.
As stated in the proof of the previous theorem, 
the reason is that any model of formula~(\ref{eq:ex-after}) must satisfy a formula that is closed under function expansion,
hence implying that formula~(\ref{eq:ex-before}) has a model.
In more detail, let $\varphi_s$ be the formula $\forall_{s} x. ite( x \leq 0, s(x) \teq 0, s( x ) \teq x + s( x-1 ) )$.
The rightmost conjunct 
$\exists z\typ{\fargsort{s}}. \farg{s}( z ) \teq c$ ensures 
that any model of formula~(\ref{eq:ex-after}) satisfying $s( c ) > 100$ also satisfies $\varphi_s[c/x]$.
Similarly, the nested existential $\exists z. \farg{s}( z ) \teq \farg{s}( y )-1 )$
ensures that this constraint is enforced recursively.
%Given a model $\I$ of formula~(\ref{eq:ex-after}) that interprets $c$ as $14$, it is easy to see that $\I$ also satisfies the formula:
\begin{eqnarray}
\begin{split}
s( c ) > 100 \wedge & \displaystyle\bigwedge\limits_{i=0}^{13} ( \neg c-i \leq 0 \wedge s( c-i ) \teq i + s( c-i-1 ) ) \\
                    & \wedge c-14 \leq 0 \wedge s( c-14 ) \teq 0
\end{split}
\end{eqnarray}

@@

When reading this input, 
\cvc adds the (annotated) quantified formula $\forallf{s} x.\;\, s( x ) \teq \lite( x \leq 0, 0, s( x-1 ) )$ to its list of assertions,
which after rewriting becomes $\forallf{s} x.\;\, \lite( x \leq 0, s( x ) \teq 0, s( x ) \teq s( x-1 ) )$.
If \cvc's finite model finding mode for recursive functions is enabled (using the command line parameter ``--fmf-fun"),
then it will replace its list of known assertions based on the conversion $\conv$ before checking for satisfiability.
%If the functions provided in the input are admissible, 
%then a ``satisfiable" response from the solver implies that a model exists for the original formula.
Accordingly, the solver will output an approximation of the interpretation for recursive function definitions,
that is, it may output the interpretation~(\ref{eq:approx-interp}) from Section~\ref{sec:encoding} for $s$.

Notice the option ``--fmf-fun" effectively instructs the SMT solver to assume that the functions provided by the user are admissible.
If this option is used for a set of functions definitions that is \emph{not} admissible, then the solver is not model-sound, that is, 
it may return ``satisfiable" for unsatisfiable inputs.
As such,
this option targets users who wish to determine the satisfiability of inputs that involving function definitions that are known to be consistent,
whereas it does not target users who wish to check the consistency of a set of function definitions.
